Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-03-18 ConferencePaper/DraftEdwardsWoods.Rnw
Simple 400 bootstrap is run.  That is enough for sd of parameters.

#Either load or create bootstrap estimates
library(boot)
if(file.exists("System.RData")) load("System.RData") else {
 System<-boot(SubsetRECS,BootThing,400)
 save(System,"System.RData")
}
@

>>>>

#Either load or create bootstrap estimates.  Note that multicore does not work on windows machines
library(boot)
if(file.exists("System.RData")) load("System.RData") else {
 System<-boot(SubsetRECS,BootThing,400,parallel="multicore",ncpus=4)
 save(System,file="System.RData")
}
@

### 2015-03-18 ConferencePaper/DraftEdwardsWoods.tex
Simple 400 bootstrap is run.  That is enough for sd of parameters.

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:51:59 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrrrrrrr}
  \hline
 & FALSEWt & FALSEAfAm & FALSEAsian & FALSEMulti & FALSENativeAm & FALSEOther & FALSEPacific & TRUEAfAm & TRUEAsian & TRUEMulti & TRUENativeAm & TRUEOther & TRUEPacific & TRUEWt \\ 
  \hline
Mobile & 371 &  24 &   1 &   6 &   7 &   2 &   1 &   3 &   0 &   1 &   2 &   6 &   0 &  97 \\ 
  SFDetached & 5694 & 754 & 231 &  87 &  35 &  59 &  22 &   8 &   5 &  10 &  17 &  41 &   2 & 730 \\ 
  SFAttached & 544 & 121 &  48 &  14 &   9 &   8 &   1 &  10 &   0 &   2 &   3 &  12 &   1 & 105 \\ 
  SmApartment & 430 & 174 &  52 &  12 &   7 &  13 &   2 &   5 &   0 &   4 &   6 &  16 &   1 & 184 \\ 
  LgApartment & 951 & 382 & 113 &  27 &  15 &  29 &  10 &   8 &   1 &   4 &   9 &  24 &   0 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-004}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:52:15 2015
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & State & Population & Reports (per 100,000) \\ 
  \hline
1 & Alabama & 4,677,464 & 7.50 \\ 
  2 & Alaska & 688,125 & 13.01 \\ 
  3 & Arizona & 6,499,377 & 3.68 \\ 
  4 & Arkansas & 2,867,764 & 9.26 \\ 
  5 & California & 36,580,371 & 3.03 \\ 
  6 & Colorado & 4,935,213 & 1.97 \\ 
  7 & Connecticut & 3,502,932 & 20.50 \\ 
  8 & Delaware & 876,211 & 14.00 \\ 
  9 & District of Columbia & 590,074 & 14.00 \\ 
  10 & Florida & 18,423,878 & 3.93 \\ 
  11 & Georgia & 9,697,838 & 2.06 \\ 
  12 & Hawaii & 1,287,481 & 13.01 \\ 
  13 & Idaho & 1,527,506 & 9.94 \\ 
  14 & Illinois & 12,842,954 & 2.88 \\ 
  15 & Indiana & 6,388,309 & 9.14 \\ 
  16 & Iowa & 2,993,987 & 19.92 \\ 
  17 & Kansas & 2,797,375 & 10.31 \\ 
  18 & Kentucky & 4,287,931 & 7.50 \\ 
  19 & Louisiana & 4,451,513 & 9.26 \\ 
  20 & Maine & 1,319,691 & 20.50 \\ 
  21 & Maryland & 5,658,655 & 14.00 \\ 
  22 & Massachusetts & 6,543,595 & 4.51 \\ 
  23 & Michigan & 10,002,486 & 4.97 \\ 
  24 & Minnesota & 5,230,567 & 19.92 \\ 
  25 & Mississippi & 2,940,212 & 7.50 \\ 
  26 & Missouri & 5,956,335 & 4.99 \\ 
  27 & Montana & 968,035 & 9.94 \\ 
  28 & Nebraska & 1,781,949 & 10.31 \\ 
  29 & Nevada & 2,615,772 & 5.08 \\ 
  30 & New Hampshire & 1,321,872 & 20.50 \\ 
  31 & New Jersey & 8,663,398 & 2.34 \\ 
  32 & New Mexico & 1,986,763 & 5.08 \\ 
  33 & New York & 19,467,789 & 4.60 \\ 
  34 & North Carolina & 9,247,134 & 4.22 \\ 
  35 & North Dakota & 641,421 & 19.92 \\ 
  36 & Ohio & 11,528,072 & 9.14 \\ 
  37 & Oklahoma & 3,644,025 & 9.26 \\ 
  38 & Oregon & 3,782,991 & 13.01 \\ 
  39 & Pennsylvania & 12,566,368 & 1.87 \\ 
  40 & Rhode Island & 1,053,502 & 20.50 \\ 
  41 & South Carolina & 4,503,280 & 4.22 \\ 
  42 & South Dakota & 804,532 & 19.92 \\ 
  43 & Tennessee & 6,240,456 & 2.61 \\ 
  44 & Texas & 24,304,290 & 4.18 \\ 
  45 & Utah & 2,727,343 & 9.94 \\ 
  46 & Vermont & 621,049 & 20.50 \\ 
  47 & Virginia & 7,795,424 & 2.03 \\ 
  48 & Washington & 6,566,073 & 13.01 \\ 
  49 & West Virginia & 1,814,873 & 14.00 \\ 
  50 & Wisconsin & 5,627,610 & 1.81 \\ 
  51 & Wyoming & 532,981 & 9.94 \\ 
   \hline
\end{tabular}
\caption{HUD Complaints per 100,000 Population} 
\label{tab:HUDComplaints}
\end{table}
\section{Conditional Demand Estimation}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:52:15 2015

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:52:15 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 1948.2943 & 80.2307 & 24.28 & 0.0000 \\ 
  RENTHELPTRUE & 206.7350 & 84.1076 & 2.46 & 0.0140 \\ 
  StrTenureOwnLgApartment & -1392.2772 & 72.2081 & -19.28 & 0.0000 \\ 
  StrTenureOwnMobile & -1134.4416 & 53.9823 & -21.02 & 0.0000 \\ 
  StrTenureOwnSFAttached & -549.6952 & 49.0434 & -11.21 & 0.0000 \\ 
  StrTenureOwnSmApartment & -779.1076 & 89.4444 & -8.71 & 0.0000 \\ 
  StrTenureRentLgApartment & -1393.4070 & 31.1855 & -44.68 & 0.0000 \\ 
  StrTenureRentMobile & -1213.4556 & 108.7993 & -11.15 & 0.0000 \\ 
  StrTenureRentSFAttached & -856.9121 & 57.0870 & -15.01 & 0.0000 \\ 
  StrTenureRentSFDetached & -553.5699 & 38.5786 & -14.35 & 0.0000 \\ 
  StrTenureRentSmApartment & -1161.1082 & 42.1556 & -27.54 & 0.0000 \\ 
  Income & 0.0078 & 0.0003 & 29.57 & 0.0000 \\ 
  reporttot & 14.8827 & 1.8850 & 7.90 & 0.0000 \\ 
  EDUCATIONNoHS & 98.3357 & 82.3383 & 1.19 & 0.2324 \\ 
  EDUCATIONHS & 109.9418 & 77.9684 & 1.41 & 0.1585 \\ 
  EDUCATIONSomeCol & 168.9859 & 78.5995 & 2.15 & 0.0316 \\ 
  EDUCATIONAA & 171.7528 & 82.0919 & 2.09 & 0.0364 \\ 
  EDUCATIONBA & 352.1423 & 79.7827 & 4.41 & 0.0000 \\ 
  EDUCATIONMA & 369.0524 & 84.7068 & 4.36 & 0.0000 \\ 
  EDUCATIONProf & 623.5784 & 105.4315 & 5.91 & 0.0000 \\ 
  EDUCATIONPHD & 499.0001 & 115.4102 & 4.32 & 0.0000 \\ 
  URUrban & -279.5002 & 25.5669 & -10.93 & 0.0000 \\ 
  reporttot:EthRaceFALSEAfAm & -4.9338 & 4.5597 & -1.08 & 0.2793 \\ 
  reporttot:EthRaceFALSEAsian & -8.7364 & 7.7372 & -1.13 & 0.2589 \\ 
  reporttot:EthRaceFALSEMulti & -18.8675 & 9.8690 & -1.91 & 0.0559 \\ 
  reporttot:EthRaceFALSENativeAm & -14.2408 & 12.0000 & -1.19 & 0.2354 \\ 
  reporttot:EthRaceFALSEOther & 0.6991 & 12.7324 & 0.05 & 0.9562 \\ 
  reporttot:EthRaceFALSEPacific & -37.5385 & 18.1475 & -2.07 & 0.0386 \\ 
  reporttot:EthRaceTRUEAfAm & -13.9581 & 28.5075 & -0.49 & 0.6244 \\ 
  reporttot:EthRaceTRUEAsian & -16.9656 & 33.5615 & -0.51 & 0.6132 \\ 
  reporttot:EthRaceTRUEMulti & 2.8707 & 16.5903 & 0.17 & 0.8626 \\ 
  reporttot:EthRaceTRUENativeAm & -22.4893 & 35.3740 & -0.64 & 0.5249 \\ 
  reporttot:EthRaceTRUEOther & 5.1444 & 11.5405 & 0.45 & 0.6558 \\ 
  reporttot:EthRaceTRUEPacific & -34.7671 & 55.4693 & -0.63 & 0.5308 \\ 
  reporttot:EthRaceTRUEWt & -23.1538 & 5.5814 & -4.15 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Orthodox Square Foot Model} 
\label{tab:OrthoSQFT}
\end{table}

  \subsection{Single Equation Methods}
  \subsection{Multiple Equation Methods}

>>>>

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Wed Mar 18 15:05:32 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrrrrrrr}
  \hline
 & FALSEWt & FALSEAfAm & FALSEAsian & FALSEMulti & FALSENativeAm & FALSEOther & FALSEPacific & TRUEAfAm & TRUEAsian & TRUEMulti & TRUENativeAm & TRUEOther & TRUEPacific & TRUEWt \\ 
  \hline
Mobile & 371 &  24 &   1 &   6 &   7 &   2 &   1 &   3 &   0 &   1 &   2 &   6 &   0 &  97 \\ 
  SFDetached & 5694 & 754 & 231 &  87 &  35 &  59 &  22 &   8 &   5 &  10 &  17 &  41 &   2 & 730 \\ 
  SFAttached & 544 & 121 &  48 &  14 &   9 &   8 &   1 &  10 &   0 &   2 &   3 &  12 &   1 & 105 \\ 
  SmApartment & 430 & 174 &  52 &  12 &   7 &  13 &   2 &   5 &   0 &   4 &   6 &  16 &   1 & 184 \\ 
  LgApartment & 951 & 382 & 113 &  27 &  15 &  29 &  10 &   8 &   1 &   4 &   9 &  24 &   0 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-004}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Wed Mar 18 15:05:38 2015
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & State & Population & Reports (per 100,000) \\ 
  \hline
1 & Alabama & 4,677,464 & 7.50 \\ 
  2 & Alaska & 688,125 & 13.01 \\ 
  3 & Arizona & 6,499,377 & 3.68 \\ 
  4 & Arkansas & 2,867,764 & 9.26 \\ 
  5 & California & 36,580,371 & 3.03 \\ 
  6 & Colorado & 4,935,213 & 1.97 \\ 
  7 & Connecticut & 3,502,932 & 20.50 \\ 
  8 & Delaware & 876,211 & 14.00 \\ 
  9 & District of Columbia & 590,074 & 14.00 \\ 
  10 & Florida & 18,423,878 & 3.93 \\ 
  11 & Georgia & 9,697,838 & 2.06 \\ 
  12 & Hawaii & 1,287,481 & 13.01 \\ 
  13 & Idaho & 1,527,506 & 9.94 \\ 
  14 & Illinois & 12,842,954 & 2.88 \\ 
  15 & Indiana & 6,388,309 & 9.14 \\ 
  16 & Iowa & 2,993,987 & 19.92 \\ 
  17 & Kansas & 2,797,375 & 10.31 \\ 
  18 & Kentucky & 4,287,931 & 7.50 \\ 
  19 & Louisiana & 4,451,513 & 9.26 \\ 
  20 & Maine & 1,319,691 & 20.50 \\ 
  21 & Maryland & 5,658,655 & 14.00 \\ 
  22 & Massachusetts & 6,543,595 & 4.51 \\ 
  23 & Michigan & 10,002,486 & 4.97 \\ 
  24 & Minnesota & 5,230,567 & 19.92 \\ 
  25 & Mississippi & 2,940,212 & 7.50 \\ 
  26 & Missouri & 5,956,335 & 4.99 \\ 
  27 & Montana & 968,035 & 9.94 \\ 
  28 & Nebraska & 1,781,949 & 10.31 \\ 
  29 & Nevada & 2,615,772 & 5.08 \\ 
  30 & New Hampshire & 1,321,872 & 20.50 \\ 
  31 & New Jersey & 8,663,398 & 2.34 \\ 
  32 & New Mexico & 1,986,763 & 5.08 \\ 
  33 & New York & 19,467,789 & 4.60 \\ 
  34 & North Carolina & 9,247,134 & 4.22 \\ 
  35 & North Dakota & 641,421 & 19.92 \\ 
  36 & Ohio & 11,528,072 & 9.14 \\ 
  37 & Oklahoma & 3,644,025 & 9.26 \\ 
  38 & Oregon & 3,782,991 & 13.01 \\ 
  39 & Pennsylvania & 12,566,368 & 1.87 \\ 
  40 & Rhode Island & 1,053,502 & 20.50 \\ 
  41 & South Carolina & 4,503,280 & 4.22 \\ 
  42 & South Dakota & 804,532 & 19.92 \\ 
  43 & Tennessee & 6,240,456 & 2.61 \\ 
  44 & Texas & 24,304,290 & 4.18 \\ 
  45 & Utah & 2,727,343 & 9.94 \\ 
  46 & Vermont & 621,049 & 20.50 \\ 
  47 & Virginia & 7,795,424 & 2.03 \\ 
  48 & Washington & 6,566,073 & 13.01 \\ 
  49 & West Virginia & 1,814,873 & 14.00 \\ 
  50 & Wisconsin & 5,627,610 & 1.81 \\ 
  51 & Wyoming & 532,981 & 9.94 \\ 
   \hline
\end{tabular}
\caption{HUD Complaints per 100,000 Population} 
\label{tab:HUDComplaints}
\end{table}
\section{Conditional Demand Estimation}

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Wed Mar 18 15:05:38 2015

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Wed Mar 18 15:05:38 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 1944.2850 & 75.4800 & 25.76 & 0.0000 \\ 
  RENTHELPTRUE & 182.1575 & 82.5453 & 2.21 & 0.0274 \\ 
  StrTenureOwnLgApartment & -1374.2383 & 67.6666 & -20.31 & 0.0000 \\ 
  StrTenureOwnMobile & -1095.7710 & 47.1356 & -23.25 & 0.0000 \\ 
  StrTenureOwnSFAttached & -493.4629 & 52.5900 & -9.38 & 0.0000 \\ 
  StrTenureOwnSmApartment & -776.3654 & 87.1475 & -8.91 & 0.0000 \\ 
  StrTenureRentLgApartment & -1393.2440 & 30.1078 & -46.28 & 0.0000 \\ 
  StrTenureRentMobile & -1202.7143 & 95.8133 & -12.55 & 0.0000 \\ 
  StrTenureRentSFAttached & -807.0103 & 62.9410 & -12.82 & 0.0000 \\ 
  StrTenureRentSFDetached & -561.3334 & 38.9760 & -14.40 & 0.0000 \\ 
  StrTenureRentSmApartment & -1142.2015 & 41.4263 & -27.57 & 0.0000 \\ 
  Income & 0.0079 & 0.0003 & 30.04 & 0.0000 \\ 
  reporttot & 11.6455 & 2.0454 & 5.69 & 0.0000 \\ 
  EDUCATIONNoHS & 45.4843 & 77.6015 & 0.59 & 0.5578 \\ 
  EDUCATIONHS & 77.1327 & 73.4168 & 1.05 & 0.2935 \\ 
  EDUCATIONSomeCol & 131.9180 & 74.1386 & 1.78 & 0.0752 \\ 
  EDUCATIONAA & 123.6675 & 77.9407 & 1.59 & 0.1126 \\ 
  EDUCATIONBA & 330.4375 & 75.4797 & 4.38 & 0.0000 \\ 
  EDUCATIONMA & 334.8239 & 80.7072 & 4.15 & 0.0000 \\ 
  EDUCATIONProf & 585.2435 & 104.0935 & 5.62 & 0.0000 \\ 
  EDUCATIONPHD & 436.0771 & 115.7913 & 3.77 & 0.0002 \\ 
  URUrban & -232.6741 & 24.4942 & -9.50 & 0.0000 \\ 
  reporttot:EthRaceFALSEAfAm & -6.9645 & 4.4105 & -1.58 & 0.1143 \\ 
  reporttot:EthRaceFALSEAsian & -6.5949 & 8.0953 & -0.81 & 0.4153 \\ 
  reporttot:EthRaceFALSEMulti & -18.6324 & 10.3186 & -1.81 & 0.0710 \\ 
  reporttot:EthRaceFALSENativeAm & -11.9507 & 11.6925 & -1.02 & 0.3068 \\ 
  reporttot:EthRaceFALSEOther & 0.1925 & 14.9557 & 0.01 & 0.9897 \\ 
  reporttot:EthRaceFALSEPacific & -34.7044 & 19.0077 & -1.83 & 0.0679 \\ 
  reporttot:EthRaceTRUEAfAm & -18.4892 & 31.5771 & -0.59 & 0.5582 \\ 
  reporttot:EthRaceTRUEAsian & -24.6105 & 43.8328 & -0.56 & 0.5745 \\ 
  reporttot:EthRaceTRUEMulti & 4.1417 & 17.6508 & 0.23 & 0.8145 \\ 
  reporttot:EthRaceTRUENativeAm & -19.0098 & 37.4768 & -0.51 & 0.6120 \\ 
  reporttot:EthRaceTRUEOther & 5.9743 & 13.0668 & 0.46 & 0.6475 \\ 
  reporttot:EthRaceTRUEPacific & -19.2825 & 57.2286 & -0.34 & 0.7362 \\ 
  reporttot:EthRaceTRUEWt & -22.7295 & 5.5102 & -4.12 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Orthodox Square Foot Model} 
\label{tab:OrthoSQFT}
\end{table}

\begin{Schunk}
\begin{Soutput}
# weights:  290 (252 variable)
initial  value 255279175.178814 
iter  10 value 158759783.153462
iter  20 value 147734978.629459
iter  30 value 135834833.627709
iter  40 value 132987175.762559
iter  50 value 132269842.703172
iter  60 value 132062253.285192
iter  70 value 131982161.901188
iter  80 value 131927174.073165
iter  90 value 131895272.068967
iter 100 value 131868925.672645
final  value 131868925.672645 
stopped after 100 iterations
\end{Soutput}
\begin{Soutput}
Call:
multinom(formula = StrTenure ~ RENTHELP + TOTSQFT_EN + Income + 
    NHSLDMEM + reporttot + EDUCATION + reporttot + reporttot:EthRace + 
    UR, data = RECS, weights = NWEIGHT)

Coefficients:
                (Intercept) RENTHELPTRUE    TOTSQFT_EN        Income   NHSLDMEM
OwnLgApartment   -1.3808040    1.8797350 -0.0014637995  1.285291e-05 -0.3451880
OwnMobile         1.8158893   -2.9512761 -0.0017777893 -5.942269e-06  0.1529041
OwnSFAttached    -2.4077803    2.4754344 -0.0002288197 -6.344140e-06 -0.2108895
OwnSmApartment   -2.9826304    0.8501427 -0.0010120758  7.383476e-06 -0.2570713
RentLgApartment   0.8250417    3.4670900 -0.0013677145 -8.407128e-06 -0.1406245
RentMobile        0.6175719    2.4300496 -0.0023185001 -6.786343e-06  0.2163635
RentSFAttached   -2.2291010    3.6783343 -0.0011203088  1.520286e-06  0.0645405
RentSFDetached   -1.8030243    2.8958817 -0.0010143061  1.630697e-06  0.2862199
RentSmApartment  -0.2967769    3.2795483 -0.0014345714 -1.986143e-06  0.1005100
                   reporttot EDUCATIONNoHS EDUCATIONHS EDUCATIONSomeCol
OwnLgApartment   0.019880503    0.14774921  0.23712770       0.42144272
OwnMobile       -0.024051432   -0.33918510 -0.56375814      -0.54284784
OwnSFAttached    0.006725643    0.45275677  0.52194480       0.57131931
OwnSmApartment   0.002463547   -0.69929218 -0.28734880      -0.47590664
RentLgApartment -0.015553801   -0.06954818 -0.05389211       0.07306169
RentMobile      -0.017521457   -0.13628980 -0.54398528      -0.64822044
RentSFAttached   0.010917990    0.12518558 -0.01100473       0.24286692
RentSFDetached  -0.015422437    0.53717185  0.43057208       0.53281535
RentSmApartment -0.128408374    0.01523668 -0.14224343       0.04692095
                EDUCATIONAA EDUCATIONBA EDUCATIONMA EDUCATIONProf EDUCATIONPHD
OwnLgApartment   0.52229832  0.75353255  1.13834506    1.59050805   0.94367442
OwnMobile       -0.55274437 -0.96180683 -1.92704473   -0.73482246  -2.23158706
OwnSFAttached    0.56363862  0.66564938  0.83483596    0.98627268   0.87268719
OwnSmApartment  -0.40490433 -0.22878214 -0.29812714   -0.04205592   0.55040818
RentLgApartment  0.06679163  0.42446829  0.29963017    0.53434670   0.64879754
RentMobile      -0.86440977 -0.66745383 -1.38567115    0.67219521   1.34147040
RentSFAttached   0.01338672  0.14465141  0.17819711   -0.22985000   0.02300164
RentSFDetached   0.24309995  0.35007366 -0.04625938    0.37903764   0.07361758
RentSmApartment -0.04923053  0.05546657 -0.08204262    0.12289508   0.29292534
                   URUrban reporttot:EthRaceFALSEAfAm
OwnLgApartment   0.6570805               -0.056105696
OwnMobile       -0.9674963               -0.210861748
OwnSFAttached    0.8263923                0.036084995
OwnSmApartment   1.9888922                0.039560570
RentLgApartment  1.2013768               -0.005796055
RentMobile      -0.7494310               -0.225234648
RentSFAttached   0.9537916                0.107604806
RentSFDetached   0.3888769                0.121425308
RentSmApartment  1.0422443                0.115540252
                reporttot:EthRaceFALSEAsian reporttot:EthRaceFALSEMulti
OwnLgApartment                   0.11642043                -0.028896243
OwnMobile                       -0.37239676                -0.009364117
OwnSFAttached                    0.11477384                 0.016246448
OwnSmApartment                   0.01191723                 0.004991006
RentLgApartment                  0.10910339                 0.030824318
RentMobile                      -0.17017724                -0.121811195
RentSFAttached                   0.03240114                -0.002046843
RentSFDetached                  -0.03893083                 0.136103946
RentSmApartment                  0.16511968                 0.019058631
                reporttot:EthRaceFALSENativeAm reporttot:EthRaceFALSEOther
OwnLgApartment                     -0.04123330                 0.143868961
OwnMobile                           0.04318066                -0.299076412
OwnSFAttached                       0.09576023                 0.010399728
OwnSmApartment                     -0.06752926                 0.003252314
RentLgApartment                     0.03849811                 0.060504183
RentMobile                         -0.08332932                -0.044122404
RentSFAttached                      0.11794364                 0.028953135
RentSFDetached                     -0.05483029                 0.007387540
RentSmApartment                     0.14717793                 0.160029423
                reporttot:EthRaceFALSEPacific reporttot:EthRaceTRUEAfAm
OwnLgApartment                    -0.01053068                0.05233122
OwnMobile                         -0.03539041               -0.13596965
OwnSFAttached                     -0.08536773                0.24119790
OwnSmApartment                    -0.02341831               -0.02406384
RentLgApartment                    0.05311680                0.14097708
RentMobile                        -0.12032710                0.26548562
RentSFAttached                    -0.06796612                0.20839233
RentSFDetached                     0.03264203                0.19243295
RentSmApartment                   -0.31214586                0.23140671
                reporttot:EthRaceTRUEAsian reporttot:EthRaceTRUEMulti
OwnLgApartment                 -0.07895009                0.011989066
OwnMobile                      -0.77760772               -1.259699465
OwnSFAttached                  -0.09553309                0.002451215
OwnSmApartment                 -0.36867095                0.132283628
RentLgApartment                -0.08761999                0.046187798
RentMobile                     -0.61034604               -0.014858229
RentSFAttached                 -0.26230380               -0.011850993
RentSFDetached                  0.04328904                0.021276614
RentSmApartment                -2.80190304                0.234295539
                reporttot:EthRaceTRUENativeAm reporttot:EthRaceTRUEOther
OwnLgApartment                   1.638682e-01                -0.02393643
OwnMobile                        7.634675e-02                -0.08188404
OwnSFAttached                    4.546190e-02                 0.02012594
OwnSmApartment                   1.103255e-01                 0.09249212
RentLgApartment                  6.842472e-02                 0.05519402
RentMobile                      -9.102506e-01                 0.16098970
RentSFAttached                   1.337601e-01                 0.11944727
RentSFDetached                   1.203474e-05                 0.05819886
RentSmApartment                  1.303347e-01                 0.14290828
                reporttot:EthRaceTRUEPacific reporttot:EthRaceTRUEWt
OwnLgApartment                   -0.04426958            -0.064083001
OwnMobile                        -0.17456167            -0.012400010
OwnSFAttached                     0.11515548             0.036464807
OwnSmApartment                    0.01762609            -0.033773659
RentLgApartment                  -0.11190849            -0.026287123
RentMobile                       -0.17885086            -0.011035661
RentSFAttached                   -0.37461474             0.001689925
RentSFDetached                   -0.18918832            -0.031980835
RentSmApartment                   0.15462478             0.146924120

Std. Errors:
                 (Intercept) RENTHELPTRUE   TOTSQFT_EN       Income
OwnLgApartment  2.804615e-10 2.256163e-12 6.482417e-07 1.220273e-08
OwnMobile       3.642268e-10 3.238303e-14 6.160650e-07 1.748914e-08
OwnSFAttached   1.064679e-10 3.776625e-12 3.446159e-07 1.229751e-08
OwnSmApartment  3.447036e-10 1.172403e-12 8.540345e-07 1.897742e-08
RentLgApartment 1.811342e-10 1.810139e-11 3.293905e-07 9.198244e-09
RentMobile      9.374497e-10 2.179126e-11 1.307564e-06 3.403626e-08
RentSFAttached  2.925585e-10 2.192346e-11 6.326804e-07 1.590451e-08
RentSFDetached  1.756909e-10 7.432628e-12 4.092411e-07 1.078800e-08
RentSmApartment 2.656272e-10 1.358162e-11 4.915795e-07 1.230647e-08
                    NHSLDMEM    reporttot EDUCATIONNoHS  EDUCATIONHS
OwnLgApartment  5.640274e-10 2.146993e-09  2.723062e-11 9.055121e-11
OwnMobile       9.910158e-10 2.213798e-09  9.135041e-11 1.503373e-10
OwnSFAttached   2.327377e-10 7.311109e-10  1.860675e-11 4.117191e-11
OwnSmApartment  7.231066e-10 2.399937e-09  3.405395e-11 1.455696e-10
RentLgApartment 4.223747e-10 1.128101e-09  5.458379e-11 6.907118e-11
RentMobile      2.805845e-09 5.776393e-09  3.139175e-10 3.592750e-10
RentSFAttached  7.930024e-10 2.129260e-09  5.530325e-11 1.050955e-10
RentSFDetached  5.996300e-10 1.131219e-09  4.425417e-11 6.808416e-11
RentSmApartment 7.700732e-10 1.375331e-09  6.459063e-11 9.609811e-11
                EDUCATIONSomeCol  EDUCATIONAA  EDUCATIONBA  EDUCATIONMA
OwnLgApartment      7.187516e-11 3.544124e-11 3.516998e-11 1.462653e-11
OwnMobile           7.838175e-11 2.086252e-11 5.586738e-12 5.604955e-13
OwnSFAttached       2.580455e-11 8.138922e-12 1.227194e-11 2.767598e-12
OwnSmApartment      7.910184e-11 3.505417e-11 3.478754e-11 6.589822e-12
RentLgApartment     3.977788e-11 1.323680e-11 1.856447e-11 3.209177e-12
RentMobile          1.644049e-10 3.881109e-11 1.258953e-11 1.341302e-12
RentSFAttached      8.320877e-11 2.415231e-11 1.817169e-11 1.873211e-12
RentSFDetached      4.639286e-11 1.269321e-11 1.016402e-11 1.289784e-12
RentSmApartment     6.524430e-11 2.146425e-11 1.396495e-11 9.256764e-13
                EDUCATIONProf EDUCATIONPHD      URUrban
OwnLgApartment   3.218023e-12 3.619174e-12 2.178313e-10
OwnMobile        2.900884e-13 3.558890e-13 1.562943e-10
OwnSFAttached    8.074232e-13 5.458122e-13 8.266410e-11
OwnSmApartment   3.783149e-13 1.802757e-12 3.195226e-10
RentLgApartment  6.936756e-13 3.786375e-12 1.454905e-10
RentMobile       4.164229e-13 1.832576e-11 4.785908e-10
RentSFAttached   1.533925e-13 1.035860e-12 2.432163e-10
RentSFDetached   3.373356e-13 8.867578e-13 1.268780e-10
RentSmApartment  4.565830e-13 1.621815e-12 2.278170e-10
                reporttot:EthRaceFALSEAfAm reporttot:EthRaceFALSEAsian
OwnLgApartment                1.689251e-10                3.756456e-11
OwnMobile                     1.373353e-10                4.191575e-13
OwnSFAttached                 1.007404e-10                1.557180e-11
OwnSmApartment                3.634714e-10                2.761003e-12
RentLgApartment               1.599844e-10                1.815375e-11
RentMobile                    3.231039e-10                8.930719e-12
RentSFAttached                5.261382e-10                7.272405e-12
RentSFDetached                2.935850e-10                6.521536e-12
RentSmApartment               3.304033e-10                1.677059e-11
                reporttot:EthRaceFALSEMulti reporttot:EthRaceFALSENativeAm
OwnLgApartment                 4.854299e-12                   1.243352e-11
OwnMobile                      1.370957e-11                   6.146206e-11
OwnSFAttached                  5.297115e-12                   1.562180e-11
OwnSmApartment                 6.848358e-12                   7.555949e-12
RentLgApartment                9.113511e-12                   1.571004e-11
RentMobile                     1.639655e-11                   5.607545e-11
RentSFAttached                 1.188234e-11                   5.826948e-11
RentSFDetached                 2.550526e-11                   7.378500e-12
RentSmApartment                7.589725e-12                   2.511002e-11
                reporttot:EthRaceFALSEOther reporttot:EthRaceFALSEPacific
OwnLgApartment                 5.935472e-11                  5.823579e-12
OwnMobile                      1.629085e-12                  6.223891e-12
OwnSFAttached                  3.830362e-12                  7.106787e-13
OwnSmApartment                 7.023030e-12                  2.639320e-12
RentLgApartment                1.799921e-11                  4.102726e-12
RentMobile                     1.715910e-11                  2.612423e-12
RentSFAttached                 1.102086e-11                  3.929249e-13
RentSFDetached                 5.998203e-12                  3.430481e-12
RentSmApartment                1.827408e-11                  8.432855e-14
                reporttot:EthRaceTRUEAfAm reporttot:EthRaceTRUEAsian
OwnLgApartment               1.483406e-12               4.680231e-13
OwnMobile                    1.079497e-11               1.156905e-13
OwnSFAttached                2.538357e-12               2.503943e-13
OwnSmApartment               8.733343e-13               1.251831e-13
RentLgApartment              1.372835e-11               7.692726e-13
RentMobile                   7.151945e-11               7.081917e-13
RentSFAttached               7.750871e-12               2.209303e-13
RentSFDetached               1.385738e-11               2.848894e-12
RentSmApartment              1.140121e-11               1.538109e-16
                reporttot:EthRaceTRUEMulti reporttot:EthRaceTRUENativeAm
OwnLgApartment                8.158892e-12                  4.968944e-12
OwnMobile                     2.542419e-15                  5.012235e-12
OwnSFAttached                 3.364180e-12                  7.220828e-13
OwnSmApartment                6.417319e-11                  2.886251e-12
RentLgApartment               1.631473e-11                  3.963477e-12
RentMobile                    6.297691e-12                  5.380459e-13
RentSFAttached                3.429080e-12                  4.499912e-12
RentSFDetached                3.398268e-12                  1.438555e-12
RentSmApartment               3.809257e-11                  4.334738e-12
                reporttot:EthRaceTRUEOther reporttot:EthRaceTRUEPacific
OwnLgApartment                2.231910e-12                 2.454064e-13
OwnMobile                     1.173327e-11                 1.321607e-12
OwnSFAttached                 1.365850e-11                 4.698338e-13
OwnSmApartment                2.255867e-11                 3.978720e-13
RentLgApartment               1.018448e-10                 1.479809e-13
RentMobile                    3.872833e-10                 2.986741e-12
RentSFAttached                1.042841e-10                 8.703513e-14
RentSFDetached                5.365307e-11                 6.936656e-13
RentSmApartment               5.117027e-11                 2.938559e-12
                reporttot:EthRaceTRUEWt
OwnLgApartment             7.548911e-11
OwnMobile                  2.708235e-10
OwnSFAttached              6.952859e-11
OwnSmApartment             1.120952e-10
RentLgApartment            1.547004e-10
RentMobile                 9.077334e-10
RentSFAttached             1.735717e-10
RentSFDetached             1.215658e-10
RentSmApartment            3.388638e-10

Residual Deviance: 263737851 
AIC: 263738355 
\end{Soutput}
\end{Schunk}

%   \subsection{Single Equation Methods}
  \subsection{Multiple Equation Methods}
